%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    \cventry
        {Founder} % Job title
        {Grai} % Organization
        {Madison, WI} % Location
        {July 2021 to present} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Founded Grai, an open-source platform that simplifies the management of complex data systems.}
            \item {Directs a global team to develop and maintain the platform, with users from companies like Roblox, Remax, and Axios.}
            \item {Spearhead all aspects of early-stage company development, including fundraising, marketing, and product strategy.}
            \item {Successfully secured venture backing from investors like Y Combinator.}
        \end{cvitems}
        }
        
    \vspace{1em}

    \cventry
        {Lead Machine Learning Engineer} % Job title
        {Centene} % Organization
        {St. Louis, MO} % Location
        {Jun. 2019 - July 2021} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Lead machine learning engineer for the NextGen and population health initiatives at Centene, a Fortune 50 healthcare company.}
            \item {Architected and oversaw implementation of novel internal machine learning deployment platform.}
            \item {Guided a cross-functional team to develop new technologies which improved healthcare data system operations and accessibility.}
            \item {Mentored junior team members, fostering professional growth and technical excellence.}
        \end{cvitems}
        }

    \vspace{1em}
    
    \cventry
        {Lead Data Scientist} % Job title
        {CiBO Technologies} % Organization
        {St. Louis, MO} % Location
        {May 2018 - May 2019} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Directed a team at CiBO Technologies to develop data tools that improved agricultural system modeling and analysis.}
            \item {Built machine learning models to predict rainfall distribution and enhance environmental understanding at the field level.}
            \item {Created software solutions to refine agricultural data quality used in forecasting crop growth patterns.}
            \item {Led company consulting efforts with fortune 500 agricultural clients to improve crop yield and quality.}
        \end{cvitems}
        }

    \vspace{1em}
    
    \cventry
        {Data Scientist} % Job title
        {Bayer} % Organization
        {St. Louis, MO} % Location
        {Feb. 2017 - May 2018} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Member of Bayer's consumer behavior team responsible for addressing farmer needs through data-driven insights.}
            \item {Developed models to forecast customer demand, guiding sales strategies and marketing resource allocation.}
            \item {Built software responsible for allocating 10's of millions of dollars in company investment.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Senior Data Scientist} % Job title
        {Mentor Spaces} % Organization
        {St. Louis, MO} % Location
        {May 2016 - Feb. 2017} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Built core analytics systems for Mentor Spaces to aid underrepresented professionals with mentorship and career opportunities.}
            \item {Developed and deployed machine learning tools to connect students with mentors and job prospects tailored to their background.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Lead Data Scientist} % Job title
        {Bellhop} % Organization
        {Chattanooga, TN} % Location
        {Dec. 2014 - May. 2016} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Led a cross-functional team of data scientists and engineers to establish the foundational analytics and machine learning capabilities for Bellhops, a tech-enabled moving company.}
            \item {Led analytics initiatives leading to a \$13.5M Series B funding round.}
            \item {Implemented the company’s first data warehouse and developed models to forecast demand across markets.}
            \item {Developed and implemented a variety of machine learning models to optimize customer acquisition, retention, and operations.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Doctoral Candidate (all but dissertation)} % Job title
        {Drexel University} % Organization
        {Philadelphia, PA} % Location
        {Sept. 2011 - Dec. 2014} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Researched computational methods for exploring quantum systems and the role of Amyloid Beta-42 protein in the formation of Alzheimer’s disease.}
            \item {Taught introductory level physics for undergraduate engineers.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Research Assistant} % Job title
        {Helmholtz Zentrum Berlin} % Organization
        {Berlin, Germany} % Location
        {Jun. 2012 - Dec. 2012} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Conducted research at Helmholtz Zentrum Berlin as part of the German academic exchange program DAAD.}
            \item {Developed custom sensor array systems for use in cryogenic, high magnetic field environments.}
            \item {Designed \& fabricated sensor arrays, and created control \& analysis software for the sensor system.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Camp Counselor} % Job title
        {Space Camp} % Organization
        {Izmir, Turkey} % Location
        {Summer 2011} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Served as a counselor at Space Camp Turkey, fostering a passion for science and space exploration in young students from across the globe.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Office Assistant} % Job title
        {Baylor University} % Organization
        {Waco, TX} % Location
        {Sep. 2009 - May. 2011} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Worked in the physics department office assisting with administrative tasks and student support.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Research Assistant} % Job title
        {Baylor University} % Organization
        {Waco, TX} % Location
        {Jan. 2009 - May. 2011} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed and implemented a novel method for infrared beam profiling including all necessary instrumentation control and data analysis software.}
            \item {Research formed the basis for an undergraduate thesis, publications in the Journal of Applied Physics, and in the AIP conference proceedings.}
            \item {Supported by multiple grant awards and earned the Barry M. Goldwater Scholarship supporting high achieving students in the sciences.}
        \end{cvitems}
        }

    \vspace{1em}

    \cventry
        {Legal Assistant} % Job title
        {Williams Hart and Boundas Law Firm} % Organization
        {Houston, TX} % Location
        {Summer 2007 \& 2008} % Date(s)
        {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Supported litigation against GSK seeking compensation for parents of children affected by the drug Paxil.}
            \item {Collected and reviewed evidence, including medical records, depositions, and other legal documents.}
            \item {Gained firsthand exposure to case strategy and legal writing, fostering an interest in legal advocacy.}
        \end{cvitems}
        }

%   \cventry
%     {Janitor} % Job title
%     {Poutous Automechanic} % Organization
%     {Houston, TX} % Location
%     {Summer 2006} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Worked full-time as a janitor cleaning the shop and assisting mechanics.}
%         \item {Performed basic customer facing functions like vehicle intake and oil \& tire changes.}
%       \end{cvitems}
%     }

%   \cventry
%     {Busboy} % Job title
%     {Croissant Brioche} % Organization
%     {Houston, TX} % Location
%     {Jan. 2005 - May 2006} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Worked part-time after school and on weekends cleaning tables, washing dishes, and assisting the kitchen staff.}
%       \end{cvitems}
%     }

\end{cventries}
