%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
    {Founder} % Job title
    {Grai} % Organization
    {Madison, WI} % Location
    {July 2021 to present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded Grai, an open-source platform that simplifies the management of complex data systems.}
        \item {Directed an international team of developers and open-source contributors to develop the Grai platform.}
        \item {Spearhead all aspects of early-stage company development, including fundraising, marketing, and product strategy.}
        \item {Secured venture backing from investors like Y Combinator and users including Roblox, Remax, and Axios.}
        \item {Tech stack: Python, TypeScript, Postgresql, Django, React, Kubernetes, Docker, Terraform, AWS, GCP, dbt}
      \end{cvitems}
    }

  \cventry
    {Lead Machine Learning Engineer} % Job title
    {Centene} % Organization
    {St. Louis, MO} % Location
    {Jun. 2019 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead Machine Learning Engineer for NextGen and population health initiatives.}
        \item {Directed a cross-functional team of 7 data scientists and engineers to develop and propagate new technologies across the organization.}
        \item {Architected a scalable machine learning deployment and maintenance framework using Kubernetes and Argo.}
        \item {Led delivery of machine learning models to provide efficient health care outcomes.}
        \item {Tech stack: Python, MongoDB, Kubernetes, Argo, Tensorflow, Dask}
      \end{cvitems}
    }

  %---------------------------------------------------------

  \cventry
    {Lead Data Scientist} % Job title
    {CIBO Technologies} % Organization
    {St. Louis, MO} % Location
    {May 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of data scientists developing smart tooling around data validation and ingestion of incoming messy data.}
        \item {Developed new data inputs to augment Bayesian models of crop growth and yield. Including fluid flow models for rainfall distribution and light scattering corrections for leaf area.} 
        \item {Engineered field level environmental classification systems using unsupervised clustering with metric learning capabilities.}
        \item {Point engineer on company consulting efforts with fortune 500 agricultural clients to improve crop yield and quality.}
        \item {Tech stack: Python, R, Scala}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Bayer} % Organization
    {St. Louis, MO} % Location
    {Feb. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of Bayer's consumer behavior team responsible for addressing farmer needs through data-driven insights.}
        \item {Built and deployed customer demand and behavior forecasting models via GLM and tree based approaches.}
        \item {Developed generalized customer segmentation models using K-means clustering with side information.}
        \item {Point engineer responsible for deploying key customer analytics business metrics driving company wide sales strategies.}
        \item {Tech stack: Python, R, Docker, AWS}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Senior Data Scientist} % Job title
    {Mentor Spaces} % Organization
    {St. Louis, MO} % Location
    {May 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built core analytics systems for Mentor Spaces to aid underrepresented professionals with mentorship and career opportunities.}
        \item {Developed early stage BI and analytics capabilities in Metabase.}
        \item {Architected companies first data warehouse using PostgresQL, Django, and RabbitMQ.}
        \item {Deployed customized Lucene based recommendation systems to support core job recommendation functionality.}
        \item {Deployed Bayesian Multi-Armed Bandit recommender systems to provide job recommendation capabilities tailored to user preferences.}
        \item {Tech stack: Python, Django, Postgresql, RabbitMQ, Docker, AWS}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Lead Data Scientist} % Job title
    {Bellhops} % Organization
    {Chattanooga, TN} % Location
    {Dec. 2014 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a mixed team of data scientists and data engineers to develop crucial early stage company analytics capabilities.}
        \item {Responsible for analytical work leading to successful close of \$13.5 million series B funding round.}
        \item {Built out early stage BI and analytics capabilities in Chartio.}
        \item {Lead the implementation of companies first data warehouse leveraging AWS, Airflow, and SQLAlchemy.}
        \item {Developed and deployed demand forecasting models across all company market segments.}
        \item {Oversaw development of early stage machine learning capabilities leveraging NLP, alongside other traditional ML components.}
        \item {Tech stack: Python, R, Django, Postgresql, AWS, Airflow}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Doctoral Candidate (ABD)} % Job title
    {Drexel University} % Organization
    {Philadelphia, PA} % Location
    {Sept. 2011 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed computational finite element techniques to model Schroedingers Equation on arbitrary two dimensional geometries with special interest in the geometric pseudo potential on bound particles.}
        \item {Developed performant finite element system implemented (Matlab) with GPU parallelization in CUDA.}
        \item {Molecular dynamic \& conformational analysis of AB-42 protein folding and it's role in Alzheimer's formation.}
        \item {Teaching undergraduate physics for engineers.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Helmholtz Zentrum Berlin} % Organization
    {Berlin, Germany} % Location
    {Jun. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed \& instrumented custom hall sensor array for field characterization in ultra-high magnetic field, cryogenic environments.}
        \item {Wrote custom instrumentation software (Borland Delphi).}
        \item {Experimental apparatus design in 3D CAD (Solidworks).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
