%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
    {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
    {Danggeun Pay Inc. (KarrotPay)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
        \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
        \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
        \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
        \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
        \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Danggeun Market Inc.} % Organization
    {Seoul, S.Korea} % Location
    {Feb. 2021 - Mar. 2021} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Founding Member \& Director of Infrastructure Division} % Job title
    {Kasa} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed on-boarding process to guide new engineers, help them to focus on the right tasks, and set expectations to help them be successful at Infrastructure team.}
        \item {Migrated the orchestration system from DC/OS to Kubernetes which is based on AWS EKS. Managed 3 Kubernetes clusters and 300+ pods. Managed all Kubernetes manifests declaratively with Kustomize and ArgoCD.}
        \item {Designed and managed complex network configurations on AWS with 4 VPC and 100+ subnets. Separated the development network and operation network according to financial regulations. Established dedicated network connections from AWS VPC to partners' on-premise network based on AWS Direct Connect with secure connection using IPsec VPN. Provisioned OpenVPN servers with LDAP integration.}
        \item {Provisioned a observability system with Kafka, Elastic Stack(Filebeat, Heartbeat, APM Server, Logstash, Elasticsearch, Kibana). Collected log, uptime, tracing data from hosts, containers, pods and more. The ES cluster which has 9 nodes processed more than 1 billion documents per month. Wrote Terraform module to easily provision ES cluster on AWS EC2 instances.}
        \item {Provisioned a monitoring system with Kafka, Telegraf, InfluxDB, Grafana. Collected metrics from hosts, containers, pods and more. Wrote Terraform module to easily provision InfluxDB with HA on AWS EC2 instances.}
        \item {Introduced Kong API Gateway to easily connect all API microservices with a declarative management method based on Terraform and Atlantis to collaborate and audit change history.}
        \item {Provisioned the Directory Service for employee identity management based on OpenLDAP which guarantees HA with multi-master replication.}
        \item {Implemented Worker microservices consuming Kafka event topics for email, SMS, Kakaotalk and Slack notification. Developed in-house framework to easily build Kafka consumer microservice with common features including retry on failure, DLQ(Dead Letter Queue), event routing and more.}
        \item {Introduced Elastic APM to help distributed tracing, trouble-shooting and performance testing in MSA.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Architect} % Job title
    {Omnious. Co., Ltd.} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded Grai, an open-source platform that simplifies the management of complex data systems.}
        \item {Directed an international team of developers and open-source contributors to develop the Grai platform.}
        \item {Spearhead all aspects of early-stage company development, including fundraising, marketing, and product strategy.}
        \item {Secured venture backing from investors like Y Combinator and users including Roblox, Remax, and Axios.}
        \item {Tech stack: Python, TypeScript, Postgresql, Django, React, Kubernetes, Docker, Terraform, AWS, GCP, dbt}
      \end{cvitems}
    }

  \cventry
    {Lead Machine Learning Engineer} % Job title
    {Centene} % Organization
    {St. Louis, MO} % Location
    {Jun. 2019 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead Machine Learning Engineer for NextGen and population health initiatives.}
        \item {Directed a cross-functional team of 7 data scientists and engineers to develop and propagate new technologies across the organization.}
        \item {Architected a scalable machine learning deployment and maintenance framework using Kubernetes and Argo.}
        \item {Led delivery of machine learning models to provide efficient health care outcomes.}
        \item {Tech stack: Python, MongoDB, Kubernetes, Argo, Tensorflow, Dask}
      \end{cvitems}
    }

  %---------------------------------------------------------

  \cventry
    {Lead Data Scientist} % Job title
    {CIBO Technologies} % Organization
    {St. Louis, MO} % Location
    {May 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of data scientists developing smart tooling around data validation and ingestion of incoming messy data.}
        \item {Developed new data inputs to augment Bayesian models of crop growth and yield. Including fluid flow models for rainfall distribution and light scattering corrections for leaf area.} 
        \item {Engineered field level environmental classification systems using unsupervised clustering with metric learning capabilities.}
        \item {Point engineer on company consulting efforts with fortune 500 agricultural clients to improve crop yield and quality.}
        \item {Tech stack: Python, R, Scala}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Bayer} % Organization
    {St. Louis, MO} % Location
    {Feb. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of Bayer's consumer behavior team responsible for addressing farmer needs through data-driven insights.}
        \item {Built and deployed customer demand and behavior forecasting models via GLM and tree based approaches.}
        \item {Developed generalized customer segmentation models using K-means clustering with side information.}
        \item {Point engineer responsible for deploying key customer analytics business metrics driving company wide sales strategies.}
        \item {Tech stack: Python, R, Docker, AWS}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Senior Data Scientist} % Job title
    {Mentor Spaces} % Organization
    {St. Louis, MO} % Location
    {May 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built core analytics systems for Mentor Spaces to aid underrepresented professionals with mentorship and career opportunities.}
        \item {Developed early stage BI and analytics capabilities in Metabase.}
        \item {Architected companies first data warehouse using PostgresQL, Django, and RabbitMQ.}
        \item {Deployed customized Lucene based recommendation systems to support core job recommendation functionality.}
        \item {Deployed Bayesian Multi-Armed Bandit recommender systems to provide job recommendation capabilities tailored to user preferences.}
        \item {Tech stack: Python, Django, Postgresql, RabbitMQ, Docker, AWS}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Lead Data Scientist} % Job title
    {Bellhops} % Organization
    {Chattanooga, TN} % Location
    {Dec. 2014 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a mixed team of data scientists and data engineers to develop crucial early stage company analytics capabilities.}
        \item {Responsible for analytical work leading to successful close of \$13.5 million series B funding round.}
        \item {Built out early stage BI and analytics capabilities in Chartio.}
        \item {Lead the implementation of companies first data warehouse leveraging AWS, Airflow, and SQLAlchemy.}
        \item {Developed and deployed demand forecasting models across all company market segments.}
        \item {Oversaw development of early stage machine learning capabilities leveraging NLP, alongside other traditional ML components.}
        \item {Tech stack: Python, R, Django, Postgresql, AWS, Airflow}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Doctoral Candidate (ABD)} % Job title
    {Drexel University} % Organization
    {Philadelphia, PA} % Location
    {Sept. 2011 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed computational finite element techniques to model Schroedingers Equation on arbitrary two dimensional geometries with special interest in the geometric pseudo potential on bound particles.}
        \item {Developed performant finite element system implemented (Matlab) with GPU parallelization in CUDA.}
        \item {Molecular dynamic \& conformational analysis of AB-42 protein folding and it's role in Alzheimer's formation.}
        \item {Teaching undergraduate physics for engineers.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Helmholtz Zentrum Berlin} % Organization
    {Berlin, Germany} % Location
    {Jun. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed \& instrumented custom hall sensor array for field characterization in ultra-high magnetic field, cryogenic environments.}
        \item {Wrote custom instrumentation software (Borland Delphi).}
        \item {Experimental apparatus design in 3D CAD (Solidworks).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
