%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
    {Founder} % Job title
    {Grai} % Organization
    {Madison, WI} % Location
    {July 2021 to present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded Grai, an open-source platform that simplifies the management of complex data systems for businesses.}
        \item {Direct a global team to develop and maintain the platform, with users from companies like Roblox, Remax, and Axios.}
        \item {Spearhead all facets of early-stage company development, including fundraising, marketing, and product strategy, securing support from investors such as Y Combinator.}
      \end{cvitems}
    }

  \cventry
    {Lead Machine Learning Engineer} % Job title
    {Centene} % Organization
    {St. Louis, MO} % Location
    {Jun. 2019 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as the lead machine learning engineer for the NextGen and population health initiatives at Centene, a Fortune 50 health insurer.}
        \item {Guided a cross-functional team to develop new technologies which improved healthcare data system operations and accessibility.}
        \item {Architected and oversaw implementation of internal machine learning deployment capabilities.}
        \item {Oversaw project planning and collaborated with stakeholders across departments to align goals with organizational priorities.}
        \item {Mentored junior team members, fostering professional growth and technical excellence.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Lead Data Scientist} % Job title
    {CiBO Technologies} % Organization
    {St. Louis, MO} % Location
    {May 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed a team at CiBO Technologies to develop data tools that improved agricultural system modeling and analysis.}
        \item {Designed models to predict rainfall distribution and enhance environmental understanding at the field level.}
        \item {Created software solutions to refine agricultural data quality, supporting sustainable farming practices.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Bayer (formerly Monsanto)} % Organization
    {St. Louis, MO} % Location
    {Feb. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with Bayer’s consumer behavior team to analyze and address farmer needs through data-driven insights.}
        \item {Developed models to forecast customer demand, enhancing sales strategies and resource allocation valued in the 10's of millions of dollars.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Senior Data Scientist} % Job title
    {Mentor Spaces (formerly Better Weekdays)} % Organization
    {St. Louis, MO} % Location
    {May 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built foundational analytics systems for Mentor Spaces, empowering underrepresented professionals through mentorship and career opportunities.}
        \item {Designed tools to connect students with mentors and job prospects, fostering professional growth.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Lead Data Scientist} % Job title
    {Bellhops} % Organization
    {Chattanooga, TN} % Location
    {Dec. 2014 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a cross-functional team of data scientists and engineers to establish the foundational analytics and machine learning capabilities for Bellhops, a tech-enabled moving company.}
        \item {Led analytics initiatives leading to a \$13.5M Series B funding round.}
        \item {Implemented the company’s first data warehouse and developed models to forecast demand across markets.}
        \item {Developed and implemented a variety of machine learning models to optimize customer acquisition and retention.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Doctoral Candidate (ABD)} % Job title
    {Drexel University} % Organization
    {Philadelphia, PA} % Location
    {Sept. 2011 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught undergraduate engineering physics courses, emphasizing clear communication of complex concepts.}
        \item {Conducted computational research on quantum systems and studied protein folding in relation to Alzheimer’s disease.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Helmholtz Zentrum Berlin} % Organization
    {Berlin, Germany} % Location
    {Jun. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted research at Helmholtz Zentrum Berlin as part of an academic exchange program, focusing on sensor technology development.}
        \item {Designed and fabricated sensor arrays and created software for advanced data analysis.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Camp Counselor} % Job title
    {Space Camp} % Organization
    {Izmir, Turkey} % Location
    {Summer 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as a counselor at Space Camp Turkey, mentoring students from diverse cultural backgrounds fostering STEM curiosity and improving cross-cultural communication.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Office Assistant} % Job title
    {Baylor University} % Organization
    {Waco, TX} % Location
    {Sep. 2009 - May. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in the physics department office assisting with administrative tasks and student support.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Baylor University} % Organization
    {Waco, TX} % Location
    {Jan. 2009 - May. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and implemented a novel method for infrared beam profiling including all necessary instrumentation control and data analysis software.}
        \item {Research formed the basis for an undergraduate thesis, publications in the Journal of Applied Physics, and in the AIP conference proceedings.}
        \item {Supported by multiple grant awards and earned the Barry M. Goldwater Scholarship supporting high achieving students in the sciences.}
      \end{cvitems}
    }

  \cventry
    {Legal Assistant} % Job title
    {Williams Hart and Boundas Law Firm} % Organization
    {Houston, TX} % Location
    {Summer 2007 \& 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported litigation against GSK seeking compensation for parents of children affected by the drug Paxil.}
        \item {Collected and reviewed evidence, including medical records, depositions, and other legal documents.}
        \item {Gained firsthand exposure to case strategy and legal writing, fostering an interest in legal advocacy.}
      \end{cvitems}
    }

%   \cventry
%     {Janitor} % Job title
%     {Poutous Automechanic} % Organization
%     {Houston, TX} % Location
%     {Summer 2006} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Worked full-time as a janitor cleaning the shop and assisting mechanics.}
%         \item {Performed basic customer facing functions like vehicle intake and oil \& tire changes.}
%       \end{cvitems}
%     }

%   \cventry
%     {Busboy} % Job title
%     {Croissant Brioche} % Organization
%     {Houston, TX} % Location
%     {Jan. 2005 - May 2006} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Worked part-time after school and on weekends cleaning tables, washing dishes, and assisting the kitchen staff.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
